---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis Build Status](https://travis-ci.org/IndrajeetPatil/rpkgtools.svg?branch=master)](https://travis-ci.org/IndrajeetPatil/rpkgtools)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/IndrajeetPatil/rpkgtools?branch=master&svg=true)](https://ci.appveyor.com/project/IndrajeetPatil/rpkgtools)
[![CircleCI](https://circleci.com/gh/IndrajeetPatil/rpkgtools.svg?style=svg)](https://circleci.com/gh/IndrajeetPatil/rpkgtools)

# rpkgtools

The goal of `rpkgtools` is to make it easy to install and subsequently load
packages needed for development of R packages.

## Installation

You can install the `rpkgtools` from `GitHub`:

```{r eval = FALSE}
devtools::install_github("IndrajeetPatil/rpkgtools")
```

Loading the package-
```{r load}
## load rpkgtools
library(rpkgtools)
```

If and when they are released on `CRAN`, the following pacakges will also be
included-

  - attachment (<https://github.com/ThinkR-open/attachment>)
  - covrpage (<https://github.com/yonicd/covrpage>)
  - defender (<https://github.com/ropenscilabs/defender>)
  - gramr (<https://github.com/ropenscilabs/gramr>)
  - packagemetrics (<https://github.com/ropenscilabs/packagemetrics>)
  - pRojects (<https://github.com/lockedata/pRojects>)
  - revdepcheck (<https://github.com/r-lib/revdepcheck>)
  - roxygen2Comment (<https://github.com/csgillespie/roxygen2Comment>)
  - roxygen2md (<https://github.com/r-lib/roxygen2md>)
  - testdown (<https://github.com/ThinkR-open/testdown>)
  - tic (<https://github.com/ropenscilabs/tic>)

If there are other R packages that you think are important for package
development, please raise an issue or make a PR.

For a more detailed account about how to develop R packages, see the following
textbook by Hadley Wickham- <http://r-pkgs.had.co.nz/>

## Code of Conduct

Please note that the `rpkgtools` project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this
project, you agree to abide by its terms.
